Preregistration: Changes

### 2022-07-25 preregistration_changes.Rmd
- Status of paper when submitted to ICA
- major updates for revision - included multiple imputation - changed theory - include new data-set - extended discussion

---
title: "Items: English"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
      toc_depth: 3
---

@@

## Analyses

I planned to conduct also the following analyses. I the time of writing, I simply hadn't yet found the time to do so.

	- Impute missing values
	- Report CFAs for scales
	- Run analyses using factor scores

>>>>

---
title: "Preregistration: Changes"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
      toc_depth: 3
---

@@

## Imputation

Reviewer feedback required changes regarding the imputation strategy

- Before: predictive mean matching with n = 1 data-sets; now: multiple imputation (also predictive mean matching) with n = 5 data-sets.
- Before: remove participants with > 50% missing data; now: include all participants
- Before: remove variables leading to much attrition; now: include all variables

## Estimation

Positive affect and negative affect were modeled as mean scores and not as factor scores. The reason was that it wasn't possible to extract factor scores for the data set with multiple imputation.
